Energy and exergy analysis of a cruise ship

### 2017-10-13 Manuscript/Manuscript.tex
Manuscript and results update

@@

figure --> Operational mode distribution
\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.8\linewidth]{Figures/Hist_mainEngines}
	\caption{Yearly load distribution, main engines}
	\label{fig:loadME_hist}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Figures/Demand_vs_time_W}
	\caption{Energy demand during a day of operations, Winter}
	\label{fig:Demand_vs_time_W}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Figures/Demand_vs_time_S}
	\caption{Energy demand during a day of operations, Summer}
	\label{fig:Demand_vs_time_S}
\end{figure}

@@

FIGURE --> Pie, heat generated by source
FIGURE --> filled lines, heat generated by source.

Looking at Figure \ref{fig:HeatGen_hist} it is possible to appreciate the amount of heat that is recovered from on board available waste heat (cooling water and exhaust gas). It can be observed that the amount of heat recovered from the HT cooling systems is much lower than expected, with an average of around 350 kW. This value is quite unreasonable compared to the values found in the technical specifications from the yard, that go from 700 kW (when only one auxiliary engine is operated) to 4800 kW (when all main engines and two auxiliary engines are operated). 
\\
\begin{figure}
	\centering
	\includegraphics[width=0.99\linewidth]{Figures/HeatGen_hist}
	\caption{Distribution of thermal power generated from on board waste heat recovery}
	\label{fig:Hist_WHR}
\end{figure}

@@

>>>>

\subsection{Operational mode}

The ship operates in different conditions, and it can be useful to provide a separate analysis depending on the operational mode. The four operational modes identified for the selected case study, together with the conditions applied to the dataset to uniquely identify each time step to a separate operational mode, are given as follows:
\begin{description}
	\item[High speed sailing] Ship speed above 15 kn
	\item[Low speed sailing] Ship speed between 4 and 15 kn
	\item[Maneuvering] Ship speed between 2 and 4 knots OR Thrusters power larger than 0
	\item[Port stays / ship drifting] All other points
\end{description}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.8\linewidth]{Figures/Pie_operationalMode}
	\caption{Operational time by mode}
	\label{fig:opMode_pie}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.8\linewidth]{Figures/Hist_mainEngines}
	\caption{Yearly load distribution, main engines}
	\label{fig:loadME_hist}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Figures/Demand_vs_time_W}
	\caption{Energy demand during a day of operations, Winter (31 Jan)}
	\label{fig:Demand_vs_time_W}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Figures/Demand_vs_time_S}
	\caption{Energy demand during a day of operations, Summer (31 Jul)}
	\label{fig:Demand_vs_time_S}
\end{figure}

@@

Looking at Figure \ref{fig:Pie_HeatGeneration} it is possible to appreciate the amount of heat that is recovered from on board available waste heat (cooling water and exhaust gas). It can be observed that  of heat recovered from the HT cooling systems represents approximately one quarter of the total heat supply. Figure \ref{fig:TimeSeries_HeatGeneration} shows how the contribution of the HRSG and the HTHR is substantially constant throughout the year, while the auxiliary boilers are used to cover the peaks and the winter increased baseload.

\begin{figure}
	\centering
	\includegraphics[width=0.99\linewidth]{Figures/Pie_HeatGeneration}
	\caption{Share of thermal power generated from on board heat systems}
	\label{fig:Pie_HeatGeneration}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.99\linewidth]{Figures/TimeSeries_HeatGeneration}
	\caption{Time series representation of the thermal power generated from on board heat systems}
	\label{fig:TimeSeries_HeatGeneration}
\end{figure}

@@

The efficiency of the recovery systems is also shown in Figure \ref{fig:Bar_efficiencyWHR}, where we show the fraction of the total energy (exergy) lost by the cooling systems and the exhaust gas of the ship's engines. It can be noted that, even when only looking at the energy that can be recovered based on the existing systems (i.e. not including the LT cooling systems, for instance), the recovery efficiency is located at around 25-35\% depending on whether the energy or the exergy efficiency is considered. Worth noting is also the fact that the efficiency on the exhaust gas side is lowered by the fact that two of the main engines are currently not equipped with HRSGs.

\begin{figure}
	\centering
	\includegraphics[width=0.99\linewidth]{Figures/Bar_WHRefficiency}
	\caption{Energy and exergy efficiency of the WHR systems}
	\label{fig:Bar_efficiencyWHR}
\end{figure}
